\Large Bayes network classifiers for fRMI

### 2012-09-14 proposal/proposal.tex
minrochanges
spelling
proposal update

\section{Programming Language}

@@

The main motivation for chosing Python over MatLab is our familiarity with Python, its performance and its clean coding style. As an added benefit, anyone is able to reproduce our classification results even if they don't own a MatLab license.

@@

>>>>

\section{Programming Language}
\label{sec:language}

@@

The main motivation for choosing Python over MatLab is our familiarity with Python, its performance and its clean coding style. As an added benefit, anyone is able to reproduce our classification results even if they don't own a MatLab license.

@@

\begin{description}
	\item[11th - 21st September]\-\\
	Research ...
	\item[22nd - 28th September]\-\\
	Model definition ...
	\item[29th - 19th October]\-\\
	Implementation and Parameter estimation ...
	\item[20th - 22nd October]\-\\
	Preparing the presentation ...
	\item[28th October]\-\\
	Final delivery of the document and the implementation
\end{description}
